### 2019-01-03 revisions/review-responses.tex

        \question Table 3. It is not clear what ``effective cycle times'' are. 
        Please clarify.
        \begin{solution}
                The ``cycle time'' definition has been added in a first appearance in text.
        \end{solution}

        %---------------------------------------------------------------------

        \question The removal of fission products is made batch wise in the 
        described algorithms. However it is not clear how the fission products 
        with the longest ``effective cycle times'' are removed. Part of them at 
        every batch? Or all of them at the end of the  ``effective cycle 
        times''.  Please clarify. And please clarify the relation between 
        ``effective cycle times'', batches and the average time spent by a 
        fission product in the reactor.
        \begin{solution}
                All of them at the end of the cycle time, and we agree that it
                 was not best solution. To clarify this following paragraph has 
                been added:

				Current version of SaltProc only allows separate out 100\% of 
				specific elements or group of elements (e.g. Processing Groups 
				as described in Table 3) at the end
				 of the specific cycle time which means the average time spent 
				by a fission product in the core is equal cycle time. That is 
				simplification because in reality fuel salt resides approximately 
				1/2 of total time in the core and rest of the time in the primary 
				loop pipes and the heat exchanger. This approach works well for 
				fast-removing elements (gases, noble metals, protactinium) which 
				should be removed each depletion step. Unfortunately, for the 
				elements with longer cycle time (i.e. rare earths should be removed 
				every 50 days) this simplified approach leads to oscillatory 
				behavior of all major parameters. In future releases of SaltProc
				 this drawback will be eliminated by removing elements with longer 
				cycle times using different method: only mass fraction (calculated 
				separately for each reprocessing group) will be removed each 
				depletion step or batch (e.g. in the current work it was chosen 
				3 days).	
        \end{solution}

### 2019-01-03 introduction.tex
rephrasing section about continous reprocessing.

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
material moves to and from the core continuously or at specific time steps 
(batch-wise). In the batch-wise approach, the burn-up simulation stops at a given 
time and restarts with a new liquid fuel composition (after removal of discarded 
materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
batch-wise approach to simulate a continuous reprocessing and refill using a single 
or multiple unit cell. ChemTriton models salt 
treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
SCALE/TRITON depletion simulation over small time steps to simulate continuous 
reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
references \cite{zhou_fuel_2018,sheu_depletion_2013,park_whole_2015, 
jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
as well as the current work also employ a batch-wise approach.

Accounting for continuous removal or addition presents a greater challenge since it 
requires adding a term to the Bateman equations. Fiorina \emph{et al.} simulated 
\gls{MSFR} depletion with continuous fuel salt reprocessing via introducing 
``reprocessing'' time constants into ERANOS transport code \cite{fiorina_investigation_2013}. Aufiero \emph{et al.} improved SERPENT2 using similar methodology by explicitly introducing 
continuous reprocessing in the system of Bateman equations by adding effective decay and transmutation terms for the different nuclides \cite{aufiero_extended_2013}.

The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}. In his work SERPENT was 
used for solution of the matrix exponential derived from the system of the Bateman 
equations \cite{aufiero_extended_2013}. Similar approach is adopted to model true 
continuous feeds and removals using MCNP transport code listed in references 
\cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.

@@

Aufiero \emph{et al.} extended the Monte Carlo burnup code SERPENT2 and 
employed it to study the material isotopic evolution of the 
\gls{MSFR}\cite{aufiero_extended_2013}. The 
developed extension directly accounts for the effects of online fuel 
reprocessing on depletion calculations and features a reactivity control 
algorithm. The extended version of SERPENT2 was assessed against a dedicated 
version of the deterministic ERANOS-based EQL3D procedure 
\cite{ruggieri_eranos_2006, fiorina_investigation_2013} and adopted to analyze 
the \gls{MSFR} fuel salt isotopic evolution.

We employed this extended SERPENT2 for a simplified unit-cell geometry of 
thermal spectrum thorium-fueled \gls{MSBR} and have had following problems: (1) 
lack of documentation describing how to use this built-in SERPENT2 online 
reprocessing capabilities\footnote{ Some challenges in no particular order: 
mass conservation is hard to achieve; not clear when use mflow card type 0, 1 or 2; 
difference between CRAM and TTA results; etc.} 
(Discussion forum for SERPENT users is only useful 
source of information at the moment); (2) reactivity control module described in Aufiero \emph{et al.} is 
not available in the latest SERPENT 2.1.30 release; (3) infinite multiplication 
factor behavior for simplified unit-cell model obtained using SERPENT2 built-in 
capabilities \cite{rykhlevskii_online_2017} does not match with exist MCNP6/Python-script
 results for the similar model by Jeong and Park\footnote{ In our 
study k$_{\infty}$ drops from 1.05 to 1.005 during a 1200 days of depletion simulation 
while in Jeong and Park work this parameter decreasing slowly from 1.065 to 1.05 for the 
similar time-frame.} \cite{jeong_equilibrium_2016}; (4) only few publication \cite{aufiero_extended_2013, 
ashraf_nuclear_2018} using these capabilities are available 
which is indicative of lack of reproducibility. Nevertheless, truly continuous 
online reprocessing capabilities of SERPENT2 is desirable feature for our 
future research. However, these capabilities should be carefully verified against 
ChemTriton/SCALE or proposed SaltProc/SERPENT2 package, and could be employed 
for removal of fission products with shorter residence time (e.g., Xe, Kr) which 
have a strong negative impact on core lifetime and breeding efficiency which 
we intent to do in the nearest future.

>>>>

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
material moves to and from the core continuously or at specific time steps 
(batch-wise). In the batch-wise approach, the burn-up simulation stops at a given 
time and restarts with a new liquid fuel composition (after removal of discarded 
materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
batch-wise approach to simulate a continuous reprocessing and refill for either single 
or multiple fluid designs. ChemTriton models salt 
treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
SCALE/TRITON depletion simulation over small time steps to simulate continuous 
reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
references \cite{zhou_fuel_2018,sheu_depletion_2013,park_whole_2015, 
jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
as well as the current work also employ a batch-wise approach.

Accounting for continuous removal or addition presents a greater challenge since it 
requires adding a term to the Bateman equations. Fiorina \emph{et al.} simulated 
\gls{MSFR} depletion with continuous fuel salt reprocessing via introducing 
``reprocessing'' time constants into the ERANOS transport code 
\cite{fiorina_investigation_2013}. 
The latest SCALE release will also have the same functionality using truly 
continuous removals \cite{betzler_implementation_2017}. 
A similar approach is adopted to model true continuous feeds and removals using the MCNP transport code listed in references \cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.

@@

Aufiero \emph{et al.} added an undocumented 
feature to SERPENT2 
using a similar methodology by explicitly introducing 
continuous reprocessing in the system of Bateman equations and adding effective 
decay and transmutation terms for each nuclide 
\cite{aufiero_extended_2013}. This was employed to study the material isotopic evolution of the 
\gls{MSFR}\cite{aufiero_extended_2013}. The developed extension directly accounts for the effects of online fuel 
reprocessing on depletion calculations and features a reactivity control 
algorithm. The extended version of SERPENT2 was assessed against a dedicated 
version of the deterministic ERANOS-based EQL3D procedure in
\cite{ruggieri_eranos_2006, fiorina_investigation_2013} and adopted to analyze 
the \gls{MSFR} fuel salt isotopic evolution.

We employed this built-in SERPENT2 feature for a simplified unit-cell geometry of 
the thermal spectrum thorium-fueled \gls{MSBR} and found it unusable\footnote{ 
Some challenges in no particular order: mass conservation is hard to achieve; 
three types of mflow cards (0, 1 or 2) are indistinguishable in purpose; an 
unexplained difference between CRAM and TTA results; etc.}. Primarily,
it is undocumented, and the discussion forum for SERPENT users is the only useful 
source of information at the moment. Additionally, the reactivity control module described in Aufiero \emph{et al.} is 
not available in the latest SERPENT 2.1.30 release. Third, the infinite multiplication 
factor behavior for simplified unit-cell model obtained using SERPENT2 built-in 
capabilities \cite{rykhlevskii_online_2017} does not match with exist MCNP6/Python-script
 results for the similar model by Jeong and Park\footnote{ In our 
study k$_{\infty}$ drops from 1.05 to 1.005 during a 1200 days of depletion simulation 
while in Jeong and Park work this parameter decreasing slowly from 1.065 to 1.05 for the 
similar time-frame.} \cite{jeong_equilibrium_2016}. Finally, only two publications \cite{aufiero_extended_2013, 
ashraf_nuclear_2018} using these capabilities are available, reflecting the 
reproducibility challenge inherent in this feature.

If these challenges can be overcome through verification against
ChemTriton/SCALE as well as this work (the SaltProc/SERPENT2 package), we hope to 
employ this SERPENT2 feature 
for removal of fission products with shorter residence time (e.g., Xe, Kr), 
since these have a strong negative impact on core lifetime and breeding 
efficiency.
